Forschungsprojekt

### 2020-07-20 documentation/paper/graphFormats.tex
a bit of progress on the paper, mainly polymer and reordering plus placehoders

\section{Graph Formats}
A rather big portion of our time was invested in figuring out which graph framework requires which graph formats. We thus decided to give an overview over all the formats we encountered, with explanation on how they represent the graph.

Additionally, to make life in the future a little bit easier, we wrote multiple tools to convert graphs acquired from Snap or Konect to the required formats. Information on how to use those tools is available in our repository.

\subsection{AdjacencyList}
The AdjacencyList and WeightedAdjacencyList formats\cite{adjListFormat} are used by Ligra and Polymer. They represent the directed edges of a graph as a number of offsets that point to a set of target nodes in the file.
First the file contains the number of vertices $n$ and edges $m$, followed by an offset for each vertex. This offset specifies at what point in the following list of numbers the information for a node begins.
Lastly the file format contains a list of target nodes.
The numbers are all separated by newlines.
\begin{gather*}
n\\
m\\
o_1\\
o_2\\
\vdots\\
o_n\\
t_1\\
t_2\\
\vdots\\
t_m
\end{gather*}
The offsets $o_i=k$ and $o_{i+1}=k+j$ mean that vertex $i$ has $j$ outgoing edges, these edges are
\begin{equation*}
	(i,t_k),(i,t_{k+1}),\ldots,(i,t_{k+j-1})
\end{equation*}

@@

\subsection{EdgeList}
The EdgeList format is probably the easiest to understand and is one of the most commonly used in the online graph repositories. The directed eges $(s_1,t_1),(s_2,t_2),\ldots$ are represented in the following way.
\begin{align*}
	&s_1,t_1\\
	&s_2,t_2\\
	&\quad\vdots\\
	&s_m,t_m
\end{align*}

\subsection{Binary EdgeList}
The binary EdgeList format is used by Gemini. Finding information on this format required reverse engineering of the Gemini code.

@@

\subsection{?}

>>>>

\subsection{An overview of some graph formats}
A rather big portion of our time was invested in figuring out which graph framework requires which graph formats. We thus decided to give an overview over all the formats we encountered, with explanation on how they represent the graph.

Additionally, to make life in the future a little bit easier, we wrote multiple tools to convert graphs acquired from Snap or Konect to the required formats. Additional information on this is available in the section \nameref{supplementaryData} at the end.

\subsubsection{AdjacencyList}
The AdjacencyList and WeightedAdjacencyList formats\cite{adjListFormat} are used by Ligra and Polymer. They represent the directed edges of a graph as a number of offsets that point to a set of target nodes in the file.
First the file contains the number of vertices $n$ and edges $m$, followed by an offset for each vertex. This offset specifies at what point in the following list of numbers the information for a node begins.
Lastly the file format contains a list of target nodes.
The numbers are all separated by newlines.
\begin{gather*}
n\\
m\\
o_1\\
o_2\\
\vdots\\
o_n\\
t_1\\
t_2\\
\vdots\\
t_m
\end{gather*}
The offsets $o_i=k$ and $o_{i+1}=k+j$ mean that vertex $i$ has $j$ outgoing edges, these edges are
\begin{equation*}
	(i,t_k),(i,t_{k+1}),\ldots,(i,t_{k+j-1})
\end{equation*}

@@

\subsubsection{EdgeList}
The EdgeList format is probably the easiest to understand and is one of the most commonly used in the online graph repositories. The directed eges $(s_1,t_1),(s_2,t_2),\ldots$ are represented in the following way.
\begin{align*}
	&s_1,t_1\\
	&s_2,t_2\\
	&\quad\vdots\\
	&s_m,t_m
\end{align*}

\subsubsection{Binary EdgeList}
The binary EdgeList format is used by Gemini. Finding information on this format required reverse engineering of the Gemini code.

@@

\subsubsection{Giraph's numerous I/O formats}

### 2020-07-20 documentation/paper/main.tex
a bit of progress on the paper, mainly polymer and reordering plus placehoders

@@

\begin{abstract}
In this paper we will analyze and compare the graph frameworks Galois, Ligra and Polymer in their parformance. We will also set up and compare these frameworks in a distributed scenario.
\end{abstract}

\begin{IEEEkeywords}
Galois, Ligra, Polymer, distributed computing, Gluon
\end{IEEEkeywords}

\section{Introduction}
My intro... blah blah \cite{Polymer}.

\input{graphFormats}
\section{Things}
\input{galois}

@@

@@

% Das hier ist mega beschissen: 
% Beim Hinzufügen neuer Referenzen
% 1. die beiden Zeilen nach diesem Kommentar auskommentieren.
%    (gemeint ist \bibliographystyle... und \bibliography..)
%    Dann alle cache files im Ordner löschen.
% 2. Die folgenden Commands ausführen
% pdflatex main.tex
% bibtex main
% pdflatex main.tex 
%    das letzte wirft dann Fehler aber das stimmt so..
% 3. Jetzt main.bbl öffnen und den Inhalt hier drunter rein kopieren.
%    Man kann kein \input benutzen, weil main.bbl leer ist, wenn die beiden
%    Zeilen auskommentiert sind. Aber wenn sie nicht auskommentiert sind
%    kann kein PDF erzeugt werden.. Was zur Hölle denken die sich.
% 4. Die folgenden beiden Zeilen auskommentieren und pdflatex 
%    ausführen wie gewohnt.

@@

>>>>

\newcommand{\todo}{{\color{red}TODO}}

@@

\begin{abstract}
In this paper we will analyze and compare the graph frameworks Galois, Ligra, Polymer, Gemini and Giraph in their parformance. All the frameworks will be tested in shared memory and Galois, Gemini and Giraph are tested on a distributed cluster as well.
Furthermore we will give some insight on the complexity of writing custom applications based on these frameworks.
\end{abstract}

\begin{IEEEkeywords}
graphs, distributed computing, Galois, Ligra, Polymer, Giraph, Gluon
\end{IEEEkeywords}

\section{Introduction}
%\todo

This paper makes the following contributions:
\begin{itemize}
  \item 
  \item 
  \item 
  \item 
\end{itemize}

\section{Overview of the framworks}
\input{galois}

@@

\input{giraph}

\section{And}
\input{graphFormats}%hier oder supplementary data

\section{Our Testing methods}

\section{Results}

\subsection{Pure Performance-Ergebnisse}

\subsection{Komplexität Aufsetzen}

\subsection{Komplexität eigene Apps schreiben}

\section{Discussion}

@@

% Beim Hinzufügen neuer Referenzen
% 1. die beiden Zeilen nach diesem Kommentar auskommentieren.
%    (gemeint ist \bibliographystyle... und \bibliography..)
%    Dann alle cache files im Ordner löschen.
% 2. Die folgenden Commands ausführen
% pdflatex main.tex
% bibtex main
% pdflatex main.tex 
%    das letzte wirft dann Fehler aber das stimmt so..
% 3. Jetzt main.bbl öffnen und den Inhalt hier drunter rein kopieren.
%    Man kann kein \input benutzen, weil main.bbl leer ist, wenn die beiden
%    Zeilen auskommentiert sind. Aber wenn sie nicht auskommentiert sind
%    kann kein PDF erzeugt werden.. Was zur Hölle denken die sich.
% 4. Die folgenden beiden Zeilen auskommentieren und pdflatex 
%    ausführen wie gewohnt.

@@

\section*{Supplementary Data}\label{supplementaryData}
We have written a number of conversion tools and installation guides to help
users or develeopers with the use of the tested frameworks.

Everything can be retrieved on our GitHub repository
\url{http://www.github.com/serengti/Forschungsprojekt}.

For each Framework, there is a

### 2020-07-20 documentation/paper/polymer.tex
a bit of progress on the paper, mainly polymer and reordering plus placehoders

\subsection{Polymer}
Installing Polymer is straight forward.

>>>>

Polymer is very similar to Ligra, in fact Polymer inherits the programming interface from Ligra\cite{Polymer}.

Polymer aims to minimize both random and remote memory accesses by implementing NUMA- and graph-aware data layout and memory access strategies.
Specifically, Polymer co-locates graph data and the computation within NUMA-nodes to reduce remote memory accesses.
For example, Polymer eliminates remote accesses by letting threads allocate memory in their local memory node for graph topology data like vertices and edges that are only accessed by one thread.
Application-defined data with static memory locations which gets dynamically updated during computation is allocated with virtual addresses that make for a seamless cross-node data access.
Other mutable runtime states (e.g. active vertices) might be dynamically allocated in each iteration. This data is allocated in a distributed way but only accessed through a global lookup table.

%Graph analytics has been long recognized to have many random access and poor data locality. Based on the observation that sequential inter-node (i.e., remote) memory accesses have much higher bandwidth than both intra- and inter-node random ones, Polymer borrows the idea from distributed graph systems by replicating vertex data across NUMA-nodes in a lightweight way. (This essentially follows the philosophy of current multi-core OS designs by treating a large-scale machine as a distributed system). Specifically, a vertex only conducts computation on edges within the local NUMA-node and uses its replicas in other NUMA-node to initiate the computation on other edges. Unlike distributed graph systems, Polymer does not distribute application- defined data but still applies all updates to a vertex within a single copy of application-defined data. Polymer has three optimizations to improve scheduling on NUMA machines and handle different properties of graphs. First, being aware of the hierarchical parallelism and locality in NUMA machines, Polymer is extended with a hierarchical scheduler to reduce the cost for synchronizing threads on multiple NUMA-nodes. Second, inspired by vertex-cuts from distributed graph systems, Polymer improves the balance of workload among NUMA-nodes by evenly partitioning edges rather than vertices for skewed graphs. Finally, as most graph algorithms converge asymmetrically, using a single data structure for runtime states may drastically degrade the performance, especially for traversal algorithms on high-diameter graphs, Polymer adopts adaptive data structures boost performance.
